Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-15 surfaces-write-up/surface-write-up.tex
added some further questions and added tiff formatted pictures

\DeclareMathOperator{\supp}{Supp}
\DeclareMathOperator{\initial}{in_\prec}
\DeclareMathOperator{\gin}{gin}
\DeclareMathOperator{\Eff}{Eff}
\DeclareMathOperator{\sat}{sat}
\DeclareMathOperator{\newspan}{span}
\DeclareMathOperator{\proj}{Proj}
\DeclareMathOperator{\spec}{Spec}
\DeclareMathOperator{\Te}{T_=}
\DeclareMathOperator{\Tp}{T_+}
\DeclareMathOperator{\Tm}{T_-}
\DeclareMathOperator{\num}{p}
\DeclareMathOperator{\den}{q}
\DeclareMathOperator{\lcm}{lcm}
%\captionsetup[table]{belowskip = 4pt}

@@

>>>>

\DeclareMathOperator{\supp}{Supp}
\DeclareMathOperator{\initial}{in_\prec}
\DeclareMathOperator{\gin}{gin}
\DeclareMathOperator{\Eff}{Eff}
\DeclareMathOperator{\sat}{sat}
\DeclareMathOperator{\newspan}{span}
\DeclareMathOperator{\proj}{Proj}
\DeclareMathOperator{\spec}{Spec}
\DeclareMathOperator{\Te}{T_=}
\DeclareMathOperator{\Tp}{T_+}
\DeclareMathOperator{\Tm}{T_-}
\DeclareMathOperator{\num}{p}
\DeclareMathOperator{\den}{q}
\DeclareMathOperator{\lcm}{lcm}
\DeclareMathOperator{\Pic}{Pic}
%\captionsetup[table]{belowskip = 4pt}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% Further Questions %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}
This paper extends the work of O'Dorney on $\mathbb{P}^1$ to $\mathbb{P}^m$ and Hirzebruch Surfaces, bounding the degrees of generation and relations of canonical rings of arbitrary divisors $D$.  The methods for deducing bounds on generators and relations of $\hirz_k$ applied similar ideas to O'Dorney's method on $\mathbb{P}^1$.

We can view $\hirz_0$ as $\mathbb{P}^1\times \mathbb{P}^1$ and more generally $\hirz_k$ as a $\mathbb{P}^1$ bundle over $\mathbb{P}^1$.  One might hope that similar ideas could be generalized to all bundles.  Specifically:
\begin{question}\label{qn:general-product/bundle}
Suppose $X$ and $Y$ are schemes.  Let $D$ be a divisor on $X\times Y$ or more generally for $X$ bundles over $Y$.  Can  generated by $x_1, \ldots x_m$ and $y_1, \ldots, y_{m'}$ with ideal of relations generated by $f_1, \ldots, f_n$ and $g_1, \ldots g_{n'}$.  Then can we find a generators and relations for $X\times Y$ or more generally for $X$ bundles over $Y$?
\end{question}
An obvious obstruction to this is the fact that we critically used the fact that $\hirz_k$ has well-defined bi-degrees.  Unfortunately, in general $\Pic(X \times Y) \not \cong \Pic(X) \times \Pic(Y)$.

Alternatively, we can view $\hirz_1$ as $\mathbb{P}^2$ blown up at a point.  This suggests the following question:
\begin{question}\label{qn:general-blowup}
Given a scheme $X$ generated by $x_1, \ldots, x_m$ with ideal of relations generated by $f_1, \ldots, f_n$.  Then can we describe generators and relations of $X$ blown up at some point $P$?
\end{question}
Fortunately, the picard group of $X$ blown up at a point is the same as that of $X$ times an additional copy of $\bz$.  Perhaps analyzing the argument from \ref{Hirzebruch-generators/relations} in the case of $\hirz_k$ from the perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by the blowup, might suggest a general method for blowups.

Answering question \ref{qn:general-blowup} would in fact provide an answer for all rational surfaces, via the minimal model program for surfaces \todo{Reference}.  One might to provide an analogous result to \ref{Hirzebruch-generators/relations} in the case of all minimal surfaces:
\begin{question}\label{qn:general-minimal-surface}
Can we provide bounds on all minimal 
\end{question}
